\begin{center} \bf \sffamily \LARGE Prisoner's dilemma with stochastic payoffs\\[-1cm] \end{center}

### 2021-05-05 main.tex
ready to push

% Include discussion on each game?

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{static/expected_two_by_two_games.pdf}
\end{figure}

>>>>

Without loss of generality we set one of the entries of the payoff matrix to 0
and another one to 1. A common normalization is \(R=1\) and
\(P=0\)~\cite{Martinez2012, Roca2009}. We vary the temptation to defect \(T\)
and the risk of cooperating \(S\). We continue the discussion of the previous
section. We compare the expected payoffs to the last round payoffs over the
different social dilemmas. The results of the simulation runs are given in
Figures~\ref{fig:expected_two_by_two} and~\ref{fig:last_round_two_by_two}.

At the left up quadrat (\(S > 0\) and  \(T \leq 1\)) the individuals interact
in the harmony game at each game stage. The harmony game is a game without
tensions. The best play in the harmony game is to always cooperate. Indeed both
figures confirm this. The behaviour varies sightly at the case \(T = 1\). Now
the temptation is equal to the payoff of a cooperation and thus individuals now
tend to defect but only slightly. The cooperating rate still remains high. At
the bottom left up quadrat (\(S \leq 0\) and  \(T < 1\)) the individuals
interact in the stag hunt game at each game stage. In the stag hunt game
cooperation is still favoured. The best response of individuals is to cooperate
and this is again confirmed by both approaches.

The last two cases are those of the prisoner’s dilemma and of the snowdrift
game. At the top right quadrat we explore the snowdrift game. In the snowdrift
game individuals want to cooperate after receiving a defection and to defect
given that their opponent defected. This behavior is captured by the figures.
In the case of \(q\), cooperating after receiving a cooperation, we observe
a decrease as the suckers payoff decreases. This is to be expected. Finally,
in the right bottom quadrat individuals interact in a prisoner’s dilemma.
In the prisoner’s dilemma individuals tend to defect. In the case of direct
reciprocity cooperation can emerge, as we discussed in the previous section.
However, in the spectrum of all the different values of \(S\) and \(T\) used
here we observe this behaviour in only a handful of cases.

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=\textwidth]{static/expected_two_by_two_games.pdf}
  \caption{{\bf Evolutionary dynamics under expected payoffs for various social dilemmas.} 
  We have run several simulations of the evolutionary process described in
  section~\ref{section:model} for $T\!=\!10^7$ time steps. The graphs show how
  often the resident population chooses each combination ($p,q$) of conditional
  cooperation probabilities in the subsequent rounds. We vary the temptation
  payoff \(T \in \{-1, -0.6, -0.2,  0.2, 0.6, 1, 1.4, 1.8, 2.2, 2.6, 3\}\)
  across the \(x\) axis, and  \(S \in \{2, 1.6, 1.2, 0.8, 0.4, 0, -0.4, -0.8,
  -1.2, -1.6, -2\}\) across the \(y\) axis. Parameters: $N\!=\!100$, $c\!=\!1$,
  $\beta\!=\!1$, $\delta\!=\!0.999$.}
  \label{fig:expected_two_by_two}
\end{figure}

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=\textwidth]{static/stochastic_two_by_two_games.pdf}
  \caption{{\bf Evolutionary dynamics under last round payoffs for various social dilemmas.} 
  We have run several simulations of the evolutionary process described in
  section~\ref{section:model} for $T\!=\!10^7$ time steps. The graphs show how
  often the resident population chooses each combination ($p,q$) of conditional
  cooperation probabilities in the subsequent rounds. We vary the temptation
  payoff \(T \in \{-1, -0.6, -0.2,  0.2, 0.6, 1, 1.4, 1.8, 2.2, 2.6, 3\}\)
  across the \(x\) axis, and  \(S \in \{2, 1.6, 1.2, 0.8, 0.4, 0, -0.4, -0.8,
  -1.2, -1.6, -2\}\) across the \(y\) axis. Parameters: $N\!=\!100$, $c\!=\!1$,
  $\beta\!=\!1$, $\delta\!=\!0.999$.}
  \label{fig:last_round_two_by_two}
\end{figure}

We have discussed the expected behaviour for each social dilemma. We now want to
account the difference in the cooperation rate given the two updating payoffs.
The cooperation rates for each of the case of the social dilemmas we have used
are given in Figure~\ref{fig:cooperation_rates_two_by_two_part_one}.

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=.45\textwidth]{static/expected_two_by_two_games_cooperation.pdf}
  \includegraphics[width=.45\textwidth]{static/stochastic_two_by_two_games_cooperation.pdf}
  \caption{\textbf{Cooperation rates over various social dilemmas.} ({\bf A}) If
  players update based on their expected payoffs. ({\bf B}) If
  players update based on their last round payoffs.}\label{fig:cooperation_rates_two_by_two_part_one}
\end{figure}

So far we have explored the difference between the expected payoffs and the last
round payoffs. In order to explore further the effect of limited memory we allow
individuals to remember more. We consider the cases where individuals remember
up two interactions, and up to the last two rounds. In total we present results
for three more cases. These are the cases of the last round two rounds with
another member of the population, last round with two members of the population,
and last round two rounds with two members of the population.

Similarly to the previous examples we have run the evolutionary process for
a large number of step for each of the social dilemmas. The results remain
the same. The behavior over the different games remains the same. We note that
now there is more noise in the evolved populations. Due to space the figures
have been moved to the Appendix, however, the cooperating rates for each of
the cases are given in Figure~\ref{fig:cooperation_rates_two_by_two_part_two}.

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=.33\textwidth]{static/rounds_two_by_two_games_cooperation.pdf}
  \includegraphics[width=.33\textwidth]{static/opponents_two_by_two_games_cooperation.pdf}
  \includegraphics[width=.33\textwidth]{static/rounds_opponents_two_by_two_games_cooperation.pdf}
  \caption{\textbf{Cooperation rates over various social dilemmas for different
  limited memory payoffs.} ({\bf A}) If
  players update based on their last two rounds with another member of the population.
  ({\bf B}) If players update based on their last round with two other members of the population.
  ({\bf C}) If players update based on their last two rounds with two other members of the population.}
  \label{fig:cooperation_rates_two_by_two_part_two}
\end{figure}
